Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-06 LaTeX/response.tex

  \item Noting differences in notation between Beranger et. al (2015), Azzalini (2013), and Azzalini and Capitanio (2003), the reviewer asks
  \begin{enumerate}[i.]
    \item Regardless of the different parametrization, i.e. you used $\sigma^2 \sim IG(a, b)$ instead of $IG(\nu/2, \nu/2)$, the formula should be equivalent. It seems that there is a missing term in your formula, if not you should explain why there is such a difference and refer to where you got that expression. My suggestion is that you should explain well, with the two steps (1) and (2) above, the process construction; \\

    \begin{response}
      As discussed in the response to the Associate Editor's Major Comment 1, given the confusion shared by all reviewers, we have added clarification about the role of $b$ as a scale parameter and provided \aref{sta:otherparams} which shows the connection between our parameterization and the more standard parameterization.
    \end{response}

@@

    \item Second, in your equation (1), $Y(s)$ is a stochastic process, a random function defined on $\calD$. Mathematically speaking, what is $\bX(s)^\top$? You only say that it is ``a set of spatial covariates at site $s$'', but this is not enough. I guess that $\bX(s)^\top$ should be a vector-valued or a matrix-valued function (a vector or matrix of functions). But if so, how should the product with the vector $\beta$ be interpreted? \\

    \begin{response}
      $\bX(\bs)$ is the usual covariate vector as in multiple linear regression.
      This is now made explicit below \eref{steq:fullmodel}.
      Then the coefficient has the linear regression interpretation that an increase of one in the $j$th element of $\bX$ shifts the distribution of $Y$ by the $j$th element of $\bbeta$.
    \end{response}

@@

  \end{enumerate}

  \item The section on the spatio-temporal extension is hard to follow and the technical details are not immediate to verify, in the present form. The presentation should be simplified. Is it not much easier that you define first the AR(1) time series and then you define appropriate transformations that link these to the functional parameters of the skew-$t$ process and you clearly show that the finite dimensional distribution of the resulting process including time and space is skew-$t$? \\

  \begin{response}
    We have heeded your advice and swapped the transformation equations (now equations \eref{steq:wstar} -- \eref{steq:sigmastar}) and the latent time series definitions (now equations \eref{steq:ts-wstar} -- \eref{steq:ts-sigmastar}).
  \end{response}

  \item Section 5 Simulation study. The current session should be shortened. Furthermore the section should be divided into two parts. Before showing the performances of your method in predicting exceedances, you should show by means of a simulation study the ability of your approach when estimating the model parameters. Since that you are considering also replications over time it should be possible to estimate reasonably well the slant parameters and the degrees of freedom. It may be the case that you have to consider larger samples. Have you tried to consider alternative parameterizations? See e.g. \citet{ArellanoValle2008}. You should investigate more seriously this aspect. \\

  \begin{response}
    As mentioned in \sref{sts:simdesign}, some of the designs for the simulation study match the methods used to fit the datasets (e.g. design 2 and method 2, design 3 and method 4).
    We have provided additional clarification in \sref{sts:simdesign} that for these models, we do appear to correctly estimate the skewness parameters and degrees of freedom.
    We have also added clarification that the difficulty in assessing convergence is only relevant for models with multiple partitions (i.e. models 4 and 5) specifically for the parameters that change across partitions.
    Because the parameters in our model do appear to properly converge when the design matches the method, we did not consider a centered parameterization as in \citet{ArellanoValle2008}.
  \end{response}

@@

\end{enumerate}

\subsection*{Minor comments}

\begin{enumerate}[1.]
  \item Page 4, first paragraph of Section 2. The references \citet{Beranger2016}, \citet{Azzalini2014} page 129 and \citet{Azzalini2003}, should be added for a clearer explanation of the additive representation; \\

@@

  \begin{response}
    We have added these references to clarify the representation.
  \end{response}

  \item Page 4, equation (1). You used the symbol ``$T$'' at least 3 times, e.g. in order to denote: transposed operation, a threshold (at page 6), a time index (at page 8). Different symbols should be used to avoid confusion; \\

  \begin{response}
    \hl{Partially done. I got the $^\top$ for transposes, but I still need to change $T \rightarrow m$ for time points.}
    The revision uses $^\top$ for transposes and $n_t$ for the number of time points.
  \end{response}

  \item Page 4 below equation (1). Specify what the size of $\bX(s)^\top$ and of $\beta$ are. Are you sure that $\lambda \in \mathbb{R}$? Is it actually $\lambda \in (-1,1)$?; \\

    \begin{response}
      Below \eref{steq:fullmodel} we clarify that $X(\bs)$ and $\beta$ are $p$-vectors.
      Yes, we use the same $\lambda$ as given in equation (5.20) of \citet[p. 129]{Azzalini2014}, so $\lambda \in \calR$.
    \end{response}

@@

  \item Page 4 below equation (1). A symbol for the correlation function of the process $v(s)$ should be used, e.g $\rho(h)$, in order to justify the presence of the matrix $\Sigma$ which is obtained from $\rho(h)$; \\

    \begin{response}
      At the end of the sentence following \eref{steq:fullmodel}, we now define correlation function $\rho(\bs_1, \bs_2)$ and indicate the $\rho$ we use to populate the correlation matrix in \eref{steq:matern}.
    \end{response}

@@

  \item Page 4 below equation (2). The size of the vector and matrices should be specified. Furthermore, specify that matrix $\Sigma$ is obtained from $\rho(h)$ and this part should be jointed to equation (3) for brevity. Finally $\Omega$ is the dispersion matrix of $Y$; \\

  \begin{response}
    We have given the sizes of the vectors and matrices below equation \eref{steq:stazzalini} (previously equation (2)). Based on the Minor Comment 4, we have now moved the $\rho(h)$ specification to \eref{steq:matern}, and we now indicate after \eref{steq:stazzalini} that $\bSigma$ is obtained from $\rho(h)$.
  \end{response}

@@

  \item Page 5, equation (3). What does $|| \cdot ||$ mean? \\

  \begin{response}
    As we now clarify below \eref{steq:matern}, this is the Euclidean distance between locations $\bs_1$ and $\bs_2$.
  \end{response}

  \item Page 5, equation (4). Since you are specifically referring to the skew-$t$ process, why don't you simply say that $c^∗ = +\infty$? You should also confirm once more that for all given $\bs \in \calD$, $Y(\bs)$ is a skew-$t$ random variable, to avoid confusion; \\

  \begin{response}
    Here we provide a general definition which allows for a bounding density.
    We now immediately clarify below \eref{steq:chih} that for the skew-$t$ distribution, $c^* = \infty$.
  \end{response}

@@

  \item Page 8, two rows below equation (10). The elements of the sequence $w_{t1}, \ldots , w_{tK}$ should be bolded. \\

  \begin{response}
    This has been fixed
  \end{response}

  \item Page 11, Section 5, 8 lines from the bottom. You wrote ``the $v_t(s)$ terms were generated using\ldots ''. This is incorrect, $v_t(s)$ is not an observation. According to (10), $v_t(s)$ is a stochastic process. \\

  \begin{response}
    Yes, $v_t(\bs)$ is a stochastic process, and simulating data from the model requires generating $v$ at the data points from a multivariate normal distribution.
  \end{response}

@@

  \item Appendix C, you use $\mu(\cdot)$ to denote the intensity measure of the Poisson point process but then $\mu$ is also a constant in the definition of the intensity measure. You should use different symbols. \\

  \begin{response}
    We now say throughout the proof in \aref{sta:proofsamepartition} that the point process is a homogeneous Poisson process with intensity $\mu(\cdot)$.
  \end{response}
\end{enumerate}

\bibliographystyle{biom}
\bibliography{library}
